\section{Results}

% Results, conclusion, and communication of results:
% Include business problems solutions: What are the results? What are the findings
% about the problems that help decision-makers take action about the business issue?
% A discussion may be included (with a separate discussion section). You can also
% comment on the quality of your results.

This report focuses on the revenue, it analyzed revenue of games from different perspectives, because developers and publishers prioritize the income. For the business, before planing and developing a game to the market, they should analyze the existed products to lower the risk of business. The Steam, as the game platform, is the perfect data source, it provides long term data with several properties, which demonstrates the intelligence for potential opportunities.

The gaming market is growing. Depend on the trend of all games from 1997 to 2024, the total revenue is increasing. Even though, there are several big fluctuation, especially after pandemic. The market is always recovered in the history. As the business, they should strongly believe that the current inflation's negative effects will gone finally, because of the requirement of entertainment.

The strategy of how to develop the price should be carefully treated. During economic crisis or pandemic period, people have more leisure time to chill out, but the disposable income is also declined, so, keep the reasonable price or even lower could make the revenue be stable.

The players of all ages should be considered. Depend on the trend of games with required age. The games is suitable for all ages, which can earn more money. If the business consider to develop the restrict game, it is also reasonable, but the capacity of the market is much lower.

The gaming industry should consider the genres of games like action, adventure and RPG for more opportunities to success. The emotion and curiosity is the booster of gaming, it follows the humanity of people.

All code for this project is uploaded on \href{https://github.com/jackeen/8812_dw_A2_code}{my github}.

